% -----------------------------------------------------------------------------
%                               Acknowledgements
% -----------------------------------------------------------------------------
\newpage                                             \chapter{Acknowledgements}

Though only my name appears on the cover of this thesis, there are a number of
people who played an integral part in its production. I am forever grateful for
those  who have made this thesis possible and because of whom, my graduate
experience thus far has been one that I will cherish forever.\\\\\\\\\


My gratitude belongs to my advisor, Dr. Jeffrey Bigham. I have been amazingly
fortunate to have an advisor who gave me the freedom to explore on my own, while
also providing guidance to recover when my steps faltered.\\


My co-advisor, Dr. Henry Kautz, has always been there to listen and give advice.
I am deeply grateful to him for the long discussions that helped me sort out
many technical details of my work and for the incredible guidance he has
provided throughout my academic career.\\

I am also indebted to Walter S. Lasecki whose interactions and discourse have
proven to be the some of the most valuable ones.  As a peer, he is second to
none in compassion and guidance.\\

Most importantly, none of this would have been happened without the love,
patience and support of my family. My mother, to whom this dissertation is
dedicated to, has been a constant source of love, compassion, support and
strength.