% -----------------------------------------------------------------------------
%                                  Abstract
% -----------------------------------------------------------------------------
\newpage
\chapter{Abstract}

Traditional 3D audio systems are often used to enhance the experience of movies
and games. Their popularity has risen as more entertainment centers and
theaters are outfitted with multiple speakers to provide the immersive
experience of the content.

3D sound can actually be provided by stereo audio sources but implementations
are often not realized or are limited because of the sensitivity of human
audible perception re-quiring that the systems are properly calibrated to
provide the proper sound experience.

3D sound is often used to provide context and supplement content in both video
and games. The use of the technology has been explored in the context of user
interface design but has not been implemented in any accessible user inter-
faces. Current solutions remain linear in scope, focusing on single focus
interfaces.  Since current audible interfaces are limited to only one dimension,
users lose the ability to place sound in a 3D environment.

Irys uses binaural audio to spatially place sound in a 3D space relative to the
user. The system offers the potential of increased productivity, smoother
transitions, and a more fluid user experience.  Context switches can provide
users with known audible transitions to inform said user when focus is shifting,
preparing the user for a different application.


