% -----------------------------------------------------------------------------
%                                 Future Work
% -----------------------------------------------------------------------------
\newpage                                                  \chapter{Future Work}

3D audio interfaces present a number of exciting capabili-ties in human computer
interaction. With an initially com-pleted framework and literature review, the
immediate short-term goals for this project are to perform user studies and
performance measures on the efficacy of this type of interface as it relates to
different tasks.

The target individuals for this interface are blind and low vision users.  I
plan on performing more in-depth studies of how this interface can be used to
best enable blind people to interact with a given interface through multi-
tasking techniques afforded by independent sound objects.

Having multiple sources of audio may be distracting for a user, so evaluation on
the number of voices a user can fo-cus on, what types of information are best
presented to the user, and time locality are all other metrics of interest for
this interface.   Search and navigation within this type of interface becomes an
interesting research topic.  How can a user query infor-mation audibly.
Systems, such as Apple’s Siri and Google Voice attempt to provide an interface
for general query and answer interactions, but how can a system be built to
allow for in-depth querying of content in a spatial manner?  Should context be
provided to search or should the system only search the locality around the
user?

Most importantly, the next major focus will be on quantify-ing the benefits of
this type of interface. Metrics on goal completion on tasks in a 3D space as
compared to regular interfaces as well as throughput as measured by multi-task
capacity would assist in understanding the efficacy of this system. Finally,
we’re very excited to explore the ability of 3D audio in helping users remember
information by providing a tangible dimension to their information pro-cessing.




%-----------------------------------------------------------------------------%
\section{                  Human Computer Interaction                         }
The study of Human Computer Interaction has very well guidelines and methods
for evaluating graphic interfaces.


%-----------------------------------------------------------------------------%
\section{                  Analytics Domain                                   }



%-----------------------------------------------------------------------------%
\section{                  Human Computer Interaction                         }




